Covariate analysis of UFL-Mayo-ISB RNASeq from cerebellum

### 2016-01-11 code/Rmd/Mayo_Cerebellum_RNASeq.Rmd
Minor modifications

---
title: "Covariate analysis of UFL-Mayo-ISB RNASeq"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_document
---
```{r knit2synapse, eval=FALSE}
library(knit2synapse)
library(synapseClient)

@@

# Find PC of residual gene expression and significant covariates that are highly correlated with PCs
residualSigCovars = runPCAandPlotCorrelations(RESIDUAL.GENE_EXPRESSION, 
                                              DESIGN,
                                              'residual matrix of all adjusted design(voom-normalized)',
                                              isKeyPlot=TRUE)
```
```{r residualSigCovars.ALL, fig.width=25, fig.height=12}
residualSigCovars[["PC_res"]][[2]]$plotData
```
```{r addVarsBack}
varsToAddBackIn <- c("DiagnosisAD", "DiagnosisControl", "DiagnosisPSP", "DiagnosisPathologic Aging")
RESIDUAL.GENE_EXPRESSION = RESIDUAL.GENE_EXPRESSION + 
  VOOM.ADJUSTED.FIT$coefficients[,varsToAddBackIn] %*% t(data.matrix(DM1$design[,varsToAddBackIn]))
RESIDUAL.GENE_EXPRESSION = rownameToFirstColumn(RESIDUAL.GENE_EXPRESSION, 'ensembl_gene_id') 
```

>>>>

---
title: "Covariate analysis of UFL-Mayo-ISB RNASeq from cerebellum"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_document
---
```{r knit2synapse, eval=FALSE}
library(knit2synapse)
library(synapseClient)

@@

# Find PC of residual gene expression and significant covariates that are highly correlated with PCs
residualSigCovars = runPCAandPlotCorrelations(RESIDUAL.GENE_EXPRESSION, 
                                              DESIGN,
                                              'residual matrix of all adjusted design(voom-normalized)',
                                              isKeyPlot=TRUE)
```
```{r residualSigCovars.ALL, fig.width=25, fig.height=12}
residualSigCovars[["PC_res"]][[2]]$plotData
```
```{r addVarsBack}
varsToAddBackIn <- c("DiagnosisAD", "DiagnosisControl", "DiagnosisPSP", "DiagnosisPathologic Aging")
RESIDUAL.GENE_EXPRESSION = RESIDUAL.GENE_EXPRESSION + 
  t(data.matrix(DM1$design[,varsToAddBackIn]) %*% t(VOOM.ADJUSTED.FIT$coefficients[,varsToAddBackIn]))
RESIDUAL.GENE_EXPRESSION = rownameToFirstColumn(RESIDUAL.GENE_EXPRESSION, 'ensembl_gene_id') 
```
